Tidy data structure to support exploration and modeling of temporal-context data

### 2018-09-04 main.Rmd
added airline map

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
library(knitr)
opts_chunk$set(
  warning = FALSE, message = FALSE, echo = FALSE,
  fig.path = 'figure/', cache.path = 'cache/', fig.align = 'center', 
  fig.show = 'hold', cache = TRUE, external = TRUE, dev = "svglite"
)
read_chunk('R/demo.R')
```

@@

## U.S.A domestic flights on-time performance (2016-2017)

A dataset of on-time performance of domestic flights in U.S.A from 2016 to 2017 is studied and explored for illustration of tidy data and data pipeline.

>>>>

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
library(knitr)
opts_chunk$set(
  warning = FALSE, message = FALSE, echo = FALSE,
  fig.path = 'figure/', cache.path = 'cache/', fig.align = 'center', 
  fig.show = 'hold', cache = TRUE, external = TRUE
)
read_chunk('R/demo.R')
read_chunk('R/flights.R')
```

@@

## On-time performance flights in U.S.A

```{r load-flights-pkgs}
```

```{r load-flights}
```

```{r map-airlines}
```

A dataset of on-time performance of domestic flights in U.S.A in 2017 is studied and explored for illustration of tidy data and data pipeline.
